---
title: "STAT 327 Homework 3"
output: html_document
---

We'll grade your homework by

* opening your "hw3.Rmd" file in RStudio
* clicking "Knit HTML"
* reading the HTML output
* reading your "hw3.Rmd"

You should write R code anywhere you see an empty R code chunk. You
should write English text anywhere you see "..."; please surround it
with doubled asterisks (`**...**`) so that it will show up as boldface
and be easy for us to find.

Include reasonable labels (titles, axis labels, legends, etc.) with
each of your graphs.

Name: **Nan Yang**

Email: **nyang49@wisc.edu**

We'll use data on housing values in suburbs of Boston. They are in an
R package called "MASS." (An R package is a collection of code,
data, and documentation. "MASS" refers to the book "Modern Applied
Statistics with S." R developed from the earlier language, S.) The
MASS package comes with the default R installation, so it's already on
your computer.  However, it's not loaded into your R session by
default. So we'll load it via the `require()` command (there's nothing
for you to do here):

```{r}
require("MASS")
```

Run `?Boston` (outside this R Markdown document) to read the help page for the `Boston` data frame.

Convert the `chas` variable to a factor with labels "off" and "on" (referring to the Charles river).

```{r}
Boston$chas= factor(Boston$chas,levels = c(1,0), labels = c("on","off"))
```

How many rows are in the Boston data frame? How many columns?

```{r}
columns = ncol(Boston)
rows = nrow(Boston)
cat(sep = "", "There are ", columns, " columns", "\n")
cat(sep = "", "There are ", rows, " rows", "\n")
```

What does a row represent?

**Each row represent a unique surbub in Boston, with statistics about the basic conditions of that surbub **

What does a column represent?

**From left to right, each column represents all observations of one specific variable. In this case, it shows one basic condition of all different surbubs, which are**

**crime rate by town,** **proportion of residential land zoned for lots over 25,000 sq.ft, proportion of non-retail business acres per town, Charles River dummy variable (= 1/on if tract bounds river; 0/off otherwise;), nitrogen oxides concentration (parts per 10 million), average number of rooms per dwelling, proportion of owner-occupied units built prior to 1940, weighted mean of distances to five Boston employment centres, index of accessibility to radial highways, full-value property-tax rate per \$10,000, pupil-teacher ratio by town, 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town, lower status of the population (percent), median value of owner-occupied homes in \$1000s.**



Make a density plot (with rug) of tax rates.

```{r}
plot(density(Boston$tax))
rug(Boston$tax)
```

Describe the shape of the distribution of tax rates.

**The graph shows that it has 2 different local maxima in probability densit function, so It's a bimodel distribution with 2 peaks around 300 and 700. The spread around main mode is wider than that around smaller mode.**

Note that the distribution shape doesn't make sense in light of the rug representation of the data. Make a histogram of the tax rates.

```{r}
# overview of graph with detailed settingx
hist(Boston$tax, breaks = 100, xlim = c(0,800),freq = TRUE)

# graph with defalt setting
hist(Boston$tax)
```

Why is the second peak of the density plot so large? In what way is the rug representation of the data inadequate? Write a line or two of code to figure it out, and then explain it.

```{r}
fisrt = length(which(Boston$tax == max(Boston$tax)))
second = length(which(Boston$tax == sort(Boston$tax, decreasing = TRUE)[fisrt + 1]))
cat(sep = "", "There are ", fisrt, " occurrences of the maximum value, ", max(Boston$tax), ", and ", second, " occurrences of the second maximum value, ", sort(Boston$tax, decreasing = TRUE)[fisrt + 1],", in this histogram.", "\n")

```
**There are more occurrences of tax rate around 666 and 711 at second peak. So it's large.**
**They are represented as a single dark line with the rug, so the representation of the data is inadequate.**



Make a barplot of "chas".

```{r}
a = table(Boston$chas)
barplot(a,ylim = c(0,500))
```

How many neighborhoods are on the Charles river?

```{r}
num = length(which(Boston$chas == "on"))
cat(sep = "", "There are ", num, " neighborhoods on the Charles river.", "\n")
```

Make a single graph consisting of three plots: 

* a scatterplot of "nox" on the y-axis vs. "dis" on the x-axis 
* a (vertical) boxplot of "nox" left of the scatterplot's y-axis
* a (horizontal) boxplot of "dis" below the scatterplot's x-axis

Hint: use `layout()` with a 4x4 matrix, using the top-right 3x3 corner
for the scatterplot, leaving the bottom-left 1x1 corner blank, and
using the other parts for the boxplots.

(An optional challenge, worth 0 extra credit points: remove the axis
and plot border from each boxplot.)

```{r, fig.width=7, fig.height=7}

figure = matrix(data = c(1, 3, 3, 3, 1, 3, 3, 3, 1, 3, 3, 3, 0, 2, 2, 2), nrow = 4, ncol = 4, byrow = TRUE)
layout(figure)
left = boxplot(Boston$nox)
below = boxplot(Boston$dis, horizontal = TRUE)
scatterplot = plot(x = Boston$dis, y = Boston$nox)

```

Look into the highest-crime neighborhood by making a single graph of one column of three rows:

* Find the row number, r, of the neighborhood with the highest "crim".
* Make a density plot of "crim". Include a rug to show the data.
* Add a red circle at (x, y) = (max crime rate, 0) to make this maximum crime rate stand out.
* Make a density plot with rug of "medv", adding a red circle at (x, y) = (medv[r], 0) to see what medv corresponds to the highest crime rate.
* Repeat the last step for "ptratio".

```{r}
r = order(Boston$crim,decreasing = TRUE)[1]
cat(sep = "", " The row ", r, " is the row of the neighborhood with the highest crim.", "\n")


figure = matrix(data = c(1,2,3), nrow = 3, ncol = 1, byrow = TRUE)
layout(figure)

plot(density(Boston$crim), main = "crime rate")
points(max(Boston$crim),0, pch = 1, col = "red")
rug(Boston$crim)

plot(density(Boston$medv),main = "median value of owner-occupied homes in $1000s." )
points(Boston[["medv"]][r],0,pch = 1, col = "red")
rug(Boston$medv)

plot(density(Boston$ptratio), main = "pupil-teacher ratio by town")
points(Boston[["ptratio"]][r],0,pch = 1, col = "red")
rug(Boston$ptratio)
```

What do you notice about the ptratio and medv for the highest-crime neighborhood?

** By comparing three graphs, the highest-crime neighborhood has common(normal) pupil-teacher ratio by town but has very few number of median value of owner-occupied homes in $1000s**